Supplementary Material for Asymmetry paper

### 2020-08-11 Supplementary/Sup_mat.Rmd
Renamed folders
Folders now match their names with how things are laid out in the paper itself

```{r load data and source function Hoop Size, echo = F, include = F}
# load model data 
load("../Analyses/Experiment_3_Hoop_size/data/model_data")

@@

load("../Analyses/Experiment_3_Hoop_size/scratch/beanbagdat")
```

@@

```{r HoopSizeFacets, include=T, echo=F, fig.width = 10, fig.height = 10, fig.cap = "Each facet of this plot shows were each participant stood on each trial. The x-axis shows the different distances that participants were tested at with 0 being the point at which they were closest 50\\% from the centre. The y-axis shows the normalised standing position between the Big Hoop and the Small Hoop."}
load("../Analyses/Experiment_3_Hoop_size/scratch/df_part2_norm")
df_hoopsize <- norm_dat
rm(norm_dat)

@@

## Experiment 3: Reward
``` {r RewardLoadData, include = F, echo = F, warning = F}
load("../Analyses/Experiment_5_Unequal_Reward/scratch/data/model_data")

@@

load("../Analyses/Experiment_5_Unequal_Reward/scratch/data/df_part1")
```

@@

plt_session1Prob <- readPNG("../Figures/Experiment_4_Prob/Part2_Trial.png")
grid.raster(plt_session1Prob)

@@

plt_fig2 <- readPNG("../Figures/Experiment_4_Prob/Part2_Trial.png")
grid.raster(plt_fig2)

@@

plt_prop_fix <- readPNG("../Figures/Experiment_4_Prob/boxes_prop_CML.png")
grid.raster(plt_prop_fix)

@@

```{r ProbExpAcc, include = T, echo = F, fig.asp = .45, fig.cap = "These show the expected accuracy for each participant (black lines) plotted against $\\Delta$. The different shaded regions show the minimum (orange) and maximum (green) expected accuracy rates for all participants. $\\Delta$ is the separations at which each participant was tested rescaled to be between 0 and 1"}
plt_prop_expAcc <- readPNG("../Figures/Experiment_4_Prob/region_performance.png")
grid.raster(plt_prop_expAcc)
```

@@

### Session 1 Accuracy 
```{r probSession1, include = T, echo = F, warning = F, fig.asp = .75, fig.cap = "This figure shows the rate at which participants correctly identified the target letter presented within a box placed some distance from the centre with the lines showing a logistic regression on these data."}
# load in part 1 data 
load("../Analyses/Experiment_4_Prob/scratch/new_data/Part_1_data_nar")

@@

### Modelling
#### Prior Predictive checks
```{r Prob load data, include = F, echo = F}
# load data
load("../Analyses/Experiment_4_Prob/modelling/BRMS/model_data/df_model")

>>>>

```{r load data and source function Hoop Size, echo = F, include = F}
# load model data 
load("../Analyses/Experiment_1_Hoop_size/data/model_data")

@@

load("../Analyses/Experiment_1_Hoop_size/scratch/beanbagdat")
```

@@

```{r HoopSizeFacets, include=T, echo=F, fig.width = 10, fig.height = 10, fig.cap = "Each facet of this plot shows were each participant stood on each trial. The x-axis shows the different distances that participants were tested at with 0 being the point at which they were closest 50\\% from the centre. The y-axis shows the normalised standing position between the Big Hoop and the Small Hoop."}
load("../Analyses/Experiment_1_Hoop_size/scratch/df_part2_norm")
df_hoopsize <- norm_dat
rm(norm_dat)

@@

## Experiment 3: Reward
``` {r RewardLoadData, include = F, echo = F, warning = F}
load("../Analyses/Experiment_3_Unequal_Reward/scratch/data/model_data")

@@

load("../Analyses/Experiment_3_Unequal_Reward/scratch/data/df_part1")
```

@@

plt_session1Prob <- readPNG("../Figures/Experiment_sup_Prob/Part2_Trial.png")
grid.raster(plt_session1Prob)

@@

plt_fig2 <- readPNG("../Figures/Experiment_sup_Prob/Part2_Trial.png")
grid.raster(plt_fig2)

@@

plt_prop_fix <- readPNG("../Figures/Experiment_sup_Prob/boxes_prop_CML.png")
grid.raster(plt_prop_fix)

@@

```{r ProbExpAcc, include = T, echo = F, fig.asp = .45, fig.cap = "These show the expected accuracy for each participant (black lines) plotted against $\\Delta$. The different shaded regions show the minimum (orange) and maximum (green) expected accuracy rates for all participants. $\\Delta$ is the separations at which each participant was tested rescaled to be between 0 and 1"}
plt_prop_expAcc <- readPNG("../Figures/Experiment_sup_Prob/region_performance.png")
grid.raster(plt_prop_expAcc)
```

@@

### Session 1 Accuracy 
```{r probSession1, include = T, echo = F, warning = F, fig.asp = .75, fig.cap = "This figure shows the rate at which participants correctly identified the target letter presented within a box placed some distance from the centre with the lines showing a logistic regression on these data."}
# load in part 1 data 
load("../Analyses/Experiment_sup_Prob/scratch/new_data/Part_1_data_nar")

@@

### Modelling
#### Prior Predictive checks
```{r Prob load data, include = F, echo = F}
# load data
load("../Analyses/Experiment_sup_Prob/modelling/BRMS/model_data/df_model")
